API design for machine learning software: experiences from the scikit-learn project

### 2013-06-26 paper.tex
Fix VW URL.

Recent years have witnessed a rising interest in machine learning and data mining
with applications in many fields.
With this rise comes a host of machine learning packages
(both open source and proprietary) with which \sklearn competes.
Although it can also be used through its Java API, Weka \citep{hall2009weka} is
popularly used through its graphical user interface (GUI). We argue that a GUI
lacks flexibility, makes experiments difficult to reproduce and has a high
maintenance cost from a development point of view. For these reasons, we make no
attempt to provide such a GUI in \sklearn.
Other existing machine learning packages 
such as SofiaML\footnote{\url{http://code.google.com/p/sofia-ml/}}
and Vowpal~Wabbit\footnote{\url{http://hunch.net/~vw/}}
are intended to be used as command-line tools
(and sometimes do not offer any type of API).
While these packages have the advantage
that their users are not tied to a particular programming language,
the users will find that they still need programming to process input/output,
and will do so in a variety of languages.
We argue that this makes it harder for researchers and developers
to exchange and collaborate on software.

>>>>

Recent years have witnessed a rising interest in machine learning and data mining
with applications in many fields.
With this rise comes a host of machine learning packages
(both open source and proprietary) with which \sklearn competes.
Although it can also be used through its Java API, Weka \citep{hall2009weka} is
popularly used through its graphical user interface (GUI). We argue that a GUI
lacks flexibility, makes experiments difficult to reproduce and has a high
maintenance cost from a development point of view. For these reasons, we make no
attempt to provide such a GUI in \sklearn.
Other existing machine learning packages 
such as SofiaML\footnote{\url{http://code.google.com/p/sofia-ml/}}
and Vowpal~Wabbit\footnote{\url{http://hunch.net/$\sim$vw/}}
are intended to be used as command-line tools
(and sometimes do not offer any type of API).
While these packages have the advantage
that their users are not tied to a particular programming language,
the users will find that they still need programming to process input/output,
and will do so in a variety of languages.
We argue that this makes it harder for researchers and developers
to exchange and collaborate on software.
